General purpose gene annotation using deep learning

### 2020-02-11 paper/main.tex
gene length stats

\begin{table}[!t]
\processtable{Data group statistics for all data\label{Tab:statistics_all}} {
\begin{tabular}{@{}lll@{}}
\toprule & EnsemblMetazoa & JGI Phytosome\\
\midrule
Fraction of classes  & 0.6, 0.02, 0.1, 0.2 & 0.6, 0.02, 0.1, 0.2 \\
(Intergenic, UTR, CDS, Intron) & & \\
Geenuff error rate & 0.1 (+- 0.02) & 0.3 (+- 0.02) \\
Average genome size in Gbp& 1.1 (+- 0.5) & 0.3 (+- 0.1) \\
Average gene length & 23000 (+- 5000) & 3370 (+- 50) \\
\botrule
\end{tabular}}{Values are averages across all genomes of a data group. The genome size is excluding FASTA sequences without a gene and subsequences that were masked as completely erroneous.}
\end{table}

\begin{table}[!t]
\processtable{Data group statistics for our training data\label{Tab:statistics_training}} {
\begin{tabular}{@{}lll@{}}
\toprule & EnsemblMetazoa & JGI Phytosome\\
\midrule
Fraction of classes  & 0.6, 0.02, 0.1, 0.2 & 0.6, 0.02, 0.1, 0.2 \\
(Intergenic, UTR, CDS, Intron) & & \\
Geenuff error rate & 0.1 (+- 0.02) & 0.3 (+- 0.02) \\
Average genome size in Gbp& 1.1 (+- 0.5) & 0.3 (+- 0.1) \\
Average gene length & 23000 (+- 5000) & 3370 (+- 50) \\
\botrule
\end{tabular}}{Values are averages across all genomes of a data group. The genome size is excluding FASTA sequences without a gene and subsequences that were masked as completely erroneous.}
\end{table}

>>>>

\begin{table}[!t]
\processtable{Data group statistics for all data\label{Tab:statistics_all}} {
\begin{tabular}{@{}lll@{}}
\toprule & Animals & Plants\\
\midrule
Average genome size in Gbp& 2.936 (+- 1.562) & 0.787 (+- 0.995) \\
Average gene length & 31,223 (+- 13,974)& 3,368 (+- 1,510)\\
Geenuff error rate & 0.311 (+- 0.129) & 0.351 (+- 0.249) \\
Fraction of class Intergenic  & 0.777 (+- 0.042) & 0.799 (+- 0.089) \\
Fraction of class UTR & 0.006 (+- 0.006) & 0.017 (+- 0.016) \\
Fraction of class CDS & 0.016 (+- 0.014) & 0.085 (+- 0.071) \\
Fraction of class Intron & 0.201 (+- 0.035) & 0.099 (+- 0.057) \\
\botrule
\end{tabular}}{Values are averages of the individual values of each genome in a data group. All statistics except the average gene lengths are excluding FASTA sequences without a gene and subsequences that were masked as completely erroneous. Each strand of DNA was counted seperately. The average gene length was determined by the average length of the longest transcript by cumulative exon length, which is how we query for genes during data generation. Brackets show the standart deviation.}
\end{table}

\begin{table}[!t]
\processtable{Data group statistics for our training data\label{Tab:statistics_training}} {
\begin{tabular}{@{}lll@{}}
\toprule & Animals & Plants\\
\midrule
Average genome size in Gbp& 2.489 (+- 2.073) & 0.914 (+- 0.934) \\
Average gene length & 25,672 (+- 16,605) & 3,509 (+- 906)\\
Geenuff error rate & 0.253 (+- 0.138) & 0.134 (+- 0.072) \\
Fraction of class Intergenic & 0.752 (+- 0.05) & 0.808 (+- 0.106) \\
Fraction of class UTR & 0.013 (+- 0.011) & 0.033 (+- 0.023) \\
Fraction of class CDS & 0.028 (+- 0.028) & 0.077 (+- 0.052) \\
Fraction of class Intron  & 0.207 (+- 0.023) & 0.083 (+- 0.037) \\
\botrule
\end{tabular}}{The description of Table \ref{Tab:statistics_all} applies here as well.}
\end{table}
